Checkerboards And Missing Species Combinations: Are Ecological Communities

### 2016-01-25 ManuscriptMarkDown.Rmd
Updating MacBook second time

---
title: 'Checkerboards And Missing Species Combinations: Are Ecological Communities
  Assembled By Chance?'
author: "Nicholas J. Gotelli"
date: "24 January 2016"
output:
  pdf_document: default
  html_document:
    highlight: haddock
    keep_md: yes
    theme: cerulean
  word_document: default
---

@@

>>>>

---
title: 'Checkerboards And Missing Species Combinations: Are Ecological Communities
  Assembled By Chance?'
author: "Nicholas J. Gotelli"
date: "24 January 2016"
output:
  html_document:
    highlight: tango
    keep_md: yes
    theme: cerulean
  pdf_document: default
  word_document: default
---

@@

```{r}
library(EcoSimR)
library(ggplot2)
library(reshape2)
set.seed(2016)
m <- melt(dataWiFinches)
m <- as.data.frame(cbind(rep(1:17,19),rep(1:19,each=17),m$value))

p <- ggplot( m, aes(x=V2, y=V1, fill=V3))
p + geom_tile()

```
